\artus{} -- Framework for Event-based Data Analysis in High Energy Physics

### 2015-10-28 Core/doc/latex/paper.tex
paper.tex: minor comments

\begin{figure}[t]
\centering \input{figures/analysis_steps}
\caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics, numbers taken from \cite{joram_phd}.
Data size is reduced by six orders of magnitude, the turnaround time by a factor of 10000.
I/O intensive operations are done highly parallelized in the WLCG.
The data reduction is achieved by performing the data-intensive operations only rarely and applying analysis specific event selection steps as early as possible.}
\label{figure_analysis_steps}
\end{figure}

>>>>

\begin{figure}[t]
\centering \input{figures/analysis_steps}
\caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics, numbers taken from \cite{joram_phd}.
Data size is reduced by six orders of magnitude, turnaround time by a factor of 4.
I/O intensive operations are done in highly parallel in the WLCG.
The data reduction is achieved by performing the data-intensive operations only rarely and applying sensible event selection steps as early as possible.}
\label{figure_analysis_steps}
\end{figure}
